---
title: "ANR preliminary TF activity gallery"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: hide
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 6,
  dpi = 150
)
```

# Packages

```{r packages}
INSTALL_MISSING <- TRUE

cran_pkgs <- c(
  "Seurat",
  "dplyr",
  "ggplot2",
  "patchwork",
  "ggrepel",
  "tibble",
  "tidyr",
  "rmarkdown"
)

missing_cran <- cran_pkgs[
  !vapply(
    cran_pkgs,
    requireNamespace,
    logical(1),
    quietly = TRUE
  )
]

if (length(missing_cran) > 0) {
  if (!INSTALL_MISSING) {
    stop(
      "Missing packages: ",
      paste(missing_cran, collapse = ", ")
    )
  }

  install.packages(
    missing_cran,
    repos = "https://cloud.r-project.org"
  )
}

suppressPackageStartupMessages({
  library(Seurat)
  library(dplyr)
  library(ggplot2)
  library(patchwork)
  library(ggrepel)
  library(tibble)
  library(tidyr)
})
```

# Configuration

```{r config}
SEURAT_RDS <- file.path(
  "data",
  "Integration_paravertebral_final.rds"
)

TF_TABLE <- file.path(
  "results_tf_activity",
  "TF_activity",
  "all_celltypes_CollecTRI_ULM.tsv"
)

DE_TABLE <- file.path(
  "results_tf_activity",
  "DESeq2",
  "all_celltypes_DMD_vs_CTRL.tsv"
)

CURRENT_FIG_PNG <- file.path(
  "results_tf_activity",
  "figures",
  "ANR_preliminary_snRNAseq_TF_activity.png"
)

OUTDIR <- file.path(
  "results_tf_activity",
  "figures",
  "anr_gallery"
)

dir.create(
  OUTDIR,
  recursive = TRUE,
  showWarnings = FALSE
)

TF_FOCUS <- "JUN"
TOP_N_TF <- 10
TOP_JUN_TARGETS <- 15
ACTIVITY_LIMIT <- 4

CELLTYPE_COL <- "cell_type"
CONDITION_COL <- "condition"

CELLTYPE_ORDER_REFERENCE <- c(
  "Myofibers",
  "Regenerating Myofibers",
  "Satellite cells",
  "FAPs",
  "Immune cells",
  "Endothelial",
  "Smooth muscle",
  "Tenocytes",
  "Schwann cells",
  "Neural cells",
  "Adipocytes"
)

CELLTYPE_COLORS <- c(
  "Adipocytes" = "#E8B92E",
  "Endothelial" = "#6BAFB0",
  "FAPs" = "#4E79A7",
  "Immune cells" = "#F28E2B",
  "Myofibers" = "#D95F4E",
  "Neural cells" = "#7BC96F",
  "Regenerating Myofibers" = "#F08A84",
  "Satellite cells" = "#59A14F",
  "Schwann cells" = "#B07AA1",
  "Smooth muscle" = "#A96F9C",
  "Tenocytes" = "#9C755F"
)
```

# Helpers

```{r helpers}
save_plot <- function(
  plot,
  filename,
  width = 9,
  height = 6
) {

  png_path <- file.path(
    OUTDIR,
    paste0(
      filename,
      ".png"
    )
  )

  pdf_path <- file.path(
    OUTDIR,
    paste0(
      filename,
      ".pdf"
    )
  )

  ggplot2::ggsave(
    filename = png_path,
    plot = plot,
    width = width,
    height = height,
    dpi = 300,
    bg = "white"
  )

  ggplot2::ggsave(
    filename = pdf_path,
    plot = plot,
    width = width,
    height = height,
    bg = "white"
  )

  invisible(
    c(
      png = png_path,
      pdf = pdf_path
    )
  )
}


load_collectri_static <- function(
  cache_dir = OUTDIR
) {

  collectri_url <- "https://rescued.omnipathdb.org/CollecTRI.csv"

  collectri_cache <- file.path(
    cache_dir,
    "CollecTRI_human.csv"
  )

  if (!file.exists(collectri_cache)) {

    message(
      "Downloading CollecTRI static network..."
    )

    utils::download.file(
      url = collectri_url,
      destfile = collectri_cache,
      mode = "wb",
      quiet = FALSE
    )
  }

  raw <- utils::read.csv(
    collectri_cache,
    stringsAsFactors = FALSE,
    check.names = FALSE
  )

  required_cols <- c(
    "source",
    "target",
    "weight"
  )

  missing_cols <- setdiff(
    required_cols,
    colnames(raw)
  )

  if (length(missing_cols) > 0) {
    stop(
      "Unexpected CollecTRI format. Missing columns: ",
      paste(
        missing_cols,
        collapse = ", "
      )
    )
  }

  raw %>%
    dplyr::transmute(
      source = as.character(source),
      target = as.character(target),
      mor = as.numeric(weight)
    ) %>%
    dplyr::filter(
      !is.na(source),
      !is.na(target),
      is.finite(mor),
      source != "",
      target != ""
    ) %>%
    dplyr::distinct(
      source,
      target,
      .keep_all = TRUE
    )
}


row_zscore <- function(x) {

  if (all(is.na(x))) {
    return(
      rep(
        NA_real_,
        length(x)
      )
    )
  }

  s <- stats::sd(
    x,
    na.rm = TRUE
  )

  m <- mean(
    x,
    na.rm = TRUE
  )

  if (
    !is.finite(s) ||
    s == 0
  ) {
    return(
      rep(
        0,
        length(x)
      )
    )
  }

  (x - m) / s
}


sig_stars <- function(p) {

  dplyr::case_when(
    is.na(p) ~ "",
    p < 0.001 ~ "***",
    p < 0.01 ~ "**",
    p < 0.05 ~ "*",
    TRUE ~ ""
  )
}


select_stratified_tfs <- function(
  tf_all,
  tf_focus = "JUN",
  top_n = 10,
  celltype_order
) {

  pair_rank <- tf_all %>%
    dplyr::filter(
      is.finite(estimate),
      !is.na(padj),
      padj < 0.05
    ) %>%
    dplyr::mutate(
      abs_activity = abs(estimate),
      celltype = as.character(celltype),
      source = as.character(source)
    ) %>%
    dplyr::group_by(celltype) %>%
    dplyr::arrange(
      padj,
      dplyr::desc(abs_activity),
      .by_group = TRUE
    ) %>%
    dplyr::mutate(
      cell_rank = dplyr::row_number()
    ) %>%
    dplyr::ungroup()

  focus_row <- pair_rank %>%
    dplyr::filter(
      source == tf_focus
    ) %>%
    dplyr::arrange(
      padj,
      dplyr::desc(abs_activity)
    ) %>%
    dplyr::slice_head(
      n = 1
    )

  if (nrow(focus_row) == 0) {

    focus_row <- tf_all %>%
      dplyr::filter(
        source == tf_focus,
        is.finite(estimate)
      ) %>%
      dplyr::mutate(
        abs_activity = abs(estimate),
        cell_rank = NA_integer_
      ) %>%
      dplyr::arrange(
        dplyr::desc(abs_activity)
      ) %>%
      dplyr::slice_head(
        n = 1
      )
  }

  if (nrow(focus_row) == 0) {
    stop(
      "Focus TF not found: ",
      tf_focus
    )
  }

  selected_rows <- focus_row

  selected_tfs <- unique(
    as.character(
      selected_rows$source
    )
  )

  covered_celltypes <- unique(
    as.character(
      selected_rows$celltype
    )
  )

  for (ct in celltype_order) {

    if (length(selected_tfs) >= top_n) {
      break
    }

    if (ct %in% covered_celltypes) {
      next
    }

    candidate <- pair_rank %>%
      dplyr::filter(
        celltype == ct,
        !source %in% selected_tfs
      ) %>%
      dplyr::slice_head(
        n = 1
      )

    if (nrow(candidate) == 0) {
      next
    }

    selected_rows <- dplyr::bind_rows(
      selected_rows,
      candidate
    )

    selected_tfs <- unique(
      c(
        selected_tfs,
        as.character(
          candidate$source
        )
      )
    )

    covered_celltypes <- unique(
      c(
        covered_celltypes,
        ct
      )
    )
  }

  if (length(selected_tfs) < top_n) {

    filler <- pair_rank %>%
      dplyr::filter(
        !source %in% selected_tfs
      ) %>%
      dplyr::arrange(
        cell_rank,
        padj,
        dplyr::desc(abs_activity)
      ) %>%
      dplyr::distinct(
        source,
        .keep_all = TRUE
      ) %>%
      dplyr::slice_head(
        n = top_n - length(selected_tfs)
      )

    selected_rows <- dplyr::bind_rows(
      selected_rows,
      filler
    )
  }

  selected_rows %>%
    dplyr::distinct(
      source,
      .keep_all = TRUE
    ) %>%
    dplyr::slice_head(
      n = top_n
    )
}


select_jun_targets <- function(
  de_all,
  focus_net,
  top_n = 15,
  celltype_order = NULL
) {

  jun_target_df <- de_all %>%
    dplyr::inner_join(
      focus_net,
      by = c(
        "gene" = "target"
      )
    ) %>%
    dplyr::filter(
      is.finite(stat),
      is.finite(mor)
    ) %>%
    dplyr::mutate(
      contribution = stat * mor,
      significant = !is.na(padj) & padj < 0.05,
      supportive = significant & contribution > 0
    )

  if (!is.null(celltype_order)) {

    jun_target_df <- jun_target_df %>%
      dplyr::filter(
        celltype %in% celltype_order
      )
  }

  target_rank <- jun_target_df %>%
    dplyr::group_by(gene) %>%
    dplyr::summarise(
      n_supportive = sum(
        supportive,
        na.rm = TRUE
      ),
      n_significant = sum(
        significant,
        na.rm = TRUE
      ),
      n_celltypes = dplyr::n_distinct(
        celltype[
          significant
        ]
      ),
      max_abs_contribution = max(
        abs(contribution),
        na.rm = TRUE
      ),
      mean_contribution = mean(
        contribution,
        na.rm = TRUE
      ),
      .groups = "drop"
    ) %>%
    dplyr::filter(
      n_supportive > 0
    ) %>%
    dplyr::arrange(
      dplyr::desc(n_supportive),
      dplyr::desc(n_celltypes),
      dplyr::desc(n_significant),
      dplyr::desc(max_abs_contribution),
      dplyr::desc(mean_contribution)
    )

  top_targets <- target_rank %>%
    dplyr::slice_head(
      n = top_n
    )

  list(
    jun_target_df = jun_target_df,
    target_rank = target_rank,
    top_targets = top_targets
  )
}


make_umap <- function(
  seu,
  reduction_name,
  celltype_col,
  celltype_order
) {

  emb <- as.data.frame(
    Seurat::Embeddings(
      seu,
      reduction = reduction_name
    )
  )

  colnames(emb)[1:2] <- c(
    "UMAP_1",
    "UMAP_2"
  )

  emb$celltype <- as.character(
    seu@meta.data[[celltype_col]]
  )

  plot_df <- emb %>%
    dplyr::filter(
      !is.na(celltype),
      celltype %in% celltype_order
    ) %>%
    dplyr::mutate(
      celltype = factor(
        celltype,
        levels = celltype_order
      )
    )

  ggplot2::ggplot(
    plot_df,
    ggplot2::aes(
      x = UMAP_1,
      y = UMAP_2,
      color = celltype
    )
  ) +
    ggplot2::geom_point(
      size = 0.16,
      alpha = 0.72,
      stroke = 0
    ) +
    ggplot2::scale_color_manual(
      values = CELLTYPE_COLORS,
      drop = FALSE,
      guide = ggplot2::guide_legend(
        override.aes = list(
          size = 4,
          alpha = 1
        )
      ),
      name = NULL
    ) +
    ggplot2::coord_equal() +
    ggplot2::labs(
      x = "UMAP 1",
      y = "UMAP 2",
      tag = "A"
    ) +
    ggplot2::theme_classic(
      base_size = 9
    ) +
    ggplot2::theme(
      plot.tag = ggplot2::element_text(
        face = "bold",
        size = 18
      ),
      plot.tag.position = c(
        0.01,
        0.99
      ),
      legend.position = "right",
      legend.text = ggplot2::element_text(
        size = 8.5
      ),
      axis.text = ggplot2::element_blank(),
      axis.ticks = ggplot2::element_blank(),
      plot.margin = ggplot2::margin(
        5,
        5,
        5,
        5
      )
    )
}


make_B_heatmap_raw <- function(
  tf_all,
  tf_sel,
  celltype_order,
  tag = "B"
) {

  top_tfs <- as.character(
    tf_sel$source
  )

  plot_df <- tf_all %>%
    dplyr::filter(
      source %in% top_tfs,
      celltype %in% celltype_order
    ) %>%
    dplyr::mutate(
      source = factor(
        source,
        levels = rev(top_tfs)
      ),
      celltype = factor(
        celltype,
        levels = celltype_order
      ),
      plot_estimate = pmax(
        -ACTIVITY_LIMIT,
        pmin(
          ACTIVITY_LIMIT,
          estimate
        )
      ),
      stars = sig_stars(
        padj
      )
    )

  ggplot2::ggplot(
    plot_df,
    ggplot2::aes(
      x = celltype,
      y = source,
      fill = plot_estimate
    )
  ) +
    ggplot2::geom_tile(
      color = "white",
      linewidth = 0.5
    ) +
    ggplot2::geom_text(
      ggplot2::aes(
        label = stars
      ),
      size = 3.7,
      fontface = "bold"
    ) +
    ggplot2::scale_fill_gradient2(
      low = "#2166AC",
      mid = "white",
      high = "#B2182B",
      midpoint = 0,
      limits = c(
        -ACTIVITY_LIMIT,
        ACTIVITY_LIMIT
      ),
      name = "ULM score"
    ) +
    ggplot2::labs(
      x = NULL,
      y = NULL,
      tag = tag
    ) +
    ggplot2::theme_minimal(
      base_size = 9
    ) +
    ggplot2::theme(
      plot.tag = ggplot2::element_text(
        face = "bold",
        size = 18
      ),
      plot.tag.position = c(
        0.01,
        0.99
      ),
      axis.text.x = ggplot2::element_text(
        angle = 38,
        hjust = 1
      ),
      axis.text.y = ggplot2::element_text(
        face = "bold"
      ),
      panel.grid = ggplot2::element_blank(),
      plot.margin = ggplot2::margin(
        5,
        5,
        5,
        5
      )
    )
}


make_B_heatmap_scaled <- function(
  tf_all,
  tf_sel,
  celltype_order,
  tag = "B"
) {

  top_tfs <- as.character(
    tf_sel$source
  )

  plot_df <- tf_all %>%
    dplyr::filter(
      source %in% top_tfs,
      celltype %in% celltype_order
    ) %>%
    dplyr::group_by(source) %>%
    dplyr::mutate(
      scaled_estimate = row_zscore(
        estimate
      )
    ) %>%
    dplyr::ungroup() %>%
    dplyr::mutate(
      source = factor(
        source,
        levels = rev(top_tfs)
      ),
      celltype = factor(
        celltype,
        levels = celltype_order
      ),
      stars = sig_stars(
        padj
      )
    )

  ggplot2::ggplot(
    plot_df,
    ggplot2::aes(
      x = celltype,
      y = source,
      fill = scaled_estimate
    )
  ) +
    ggplot2::geom_tile(
      color = "white",
      linewidth = 0.5
    ) +
    ggplot2::geom_text(
      ggplot2::aes(
        label = stars
      ),
      size = 3.7,
      fontface = "bold"
    ) +
    ggplot2::scale_fill_gradient2(
      low = "#2166AC",
      mid = "white",
      high = "#B2182B",
      midpoint = 0,
      limits = c(
        -2.5,
        2.5
      ),
      name = "Row-scaled
ULM score"
    ) +
    ggplot2::labs(
      x = NULL,
      y = NULL,
      tag = tag
    ) +
    ggplot2::theme_minimal(
      base_size = 9
    ) +
    ggplot2::theme(
      plot.tag = ggplot2::element_text(
        face = "bold",
        size = 18
      ),
      plot.tag.position = c(
        0.01,
        0.99
      ),
      axis.text.x = ggplot2::element_text(
        angle = 38,
        hjust = 1
      ),
      axis.text.y = ggplot2::element_text(
        face = "bold"
      ),
      panel.grid = ggplot2::element_blank(),
      plot.margin = ggplot2::margin(
        5,
        5,
        5,
        5
      )
    )
}


make_B_dotplot <- function(
  tf_all,
  tf_sel,
  celltype_order,
  tag = "B"
) {

  top_tfs <- as.character(
    tf_sel$source
  )

  plot_df <- tf_all %>%
    dplyr::filter(
      source %in% top_tfs,
      celltype %in% celltype_order
    ) %>%
    dplyr::mutate(
      source = factor(
        source,
        levels = rev(top_tfs)
      ),
      celltype = factor(
        celltype,
        levels = celltype_order
      ),
      neglog10_padj = dplyr::if_else(
        is.na(padj),
        0,
        pmin(
          10,
          -log10(
            padj + 1e-300
          )
        )
      ),
      plot_estimate = pmax(
        -ACTIVITY_LIMIT,
        pmin(
          ACTIVITY_LIMIT,
          estimate
        )
      )
    )

  ggplot2::ggplot(
    plot_df,
    ggplot2::aes(
      x = celltype,
      y = source
    )
  ) +
    ggplot2::geom_point(
      ggplot2::aes(
        size = neglog10_padj,
        color = plot_estimate
      ),
      alpha = 0.95
    ) +
    ggplot2::scale_color_gradient2(
      low = "#2166AC",
      mid = "white",
      high = "#B2182B",
      midpoint = 0,
      limits = c(
        -ACTIVITY_LIMIT,
        ACTIVITY_LIMIT
      ),
      name = "ULM score"
    ) +
    ggplot2::scale_size_continuous(
      name = "-log10(padj)",
      range = c(
        1,
        8
      )
    ) +
    ggplot2::labs(
      x = NULL,
      y = NULL,
      tag = tag
    ) +
    ggplot2::theme_minimal(
      base_size = 9
    ) +
    ggplot2::theme(
      plot.tag = ggplot2::element_text(
        face = "bold",
        size = 18
      ),
      plot.tag.position = c(
        0.01,
        0.99
      ),
      axis.text.x = ggplot2::element_text(
        angle = 38,
        hjust = 1
      ),
      axis.text.y = ggplot2::element_text(
        face = "bold"
      ),
      panel.grid.minor = ggplot2::element_blank(),
      plot.margin = ggplot2::margin(
        5,
        5,
        5,
        5
      )
    )
}


make_source_targets_plot <- function(
  jun_target_df,
  celltypes_use,
  top_label_n = 12,
  facet = TRUE,
  tag = "C"
) {

  plot_df <- jun_target_df %>%
    dplyr::filter(
      celltype %in% celltypes_use
    ) %>%
    dplyr::group_by(celltype) %>%
    dplyr::arrange(
      gene,
      .by_group = TRUE
    ) %>%
    dplyr::mutate(
      jitter_index = dplyr::row_number(),
      x_jitter = mor +
        (
          (
            jitter_index %% 9
          ) - 4
        ) * 0.025,
      sig = !is.na(padj) & padj < 0.05
    ) %>%
    dplyr::ungroup()

  label_df <- plot_df %>%
    dplyr::group_by(celltype) %>%
    dplyr::arrange(
      dplyr::desc(
        abs(contribution)
      ),
      .by_group = TRUE
    ) %>%
    dplyr::slice_head(
      n = top_label_n
    ) %>%
    dplyr::ungroup()

  p <- ggplot2::ggplot(
    plot_df,
    ggplot2::aes(
      x = x_jitter,
      y = stat
    )
  ) +
    ggplot2::geom_vline(
      xintercept = 0,
      linetype = "dashed",
      color = "grey55",
      linewidth = 0.35
    ) +
    ggplot2::geom_hline(
      yintercept = 0,
      linetype = "dashed",
      color = "grey55",
      linewidth = 0.35
    ) +
    ggplot2::geom_point(
      ggplot2::aes(
        fill = contribution,
        alpha = sig
      ),
      shape = 21,
      size = 2.6,
      color = "black",
      stroke = 0.2
    ) +
    ggrepel::geom_text_repel(
      data = label_df,
      ggplot2::aes(
        label = gene
      ),
      size = 2.7,
      box.padding = 0.25,
      point.padding = 0.15,
      max.overlaps = Inf,
      seed = 1
    ) +
    ggplot2::scale_fill_gradient2(
      low = "#2166AC",
      mid = "white",
      high = "#B2182B",
      midpoint = 0,
      name = "stat × mor"
    ) +
    ggplot2::scale_alpha_manual(
      values = c(
        "TRUE" = 0.95,
        "FALSE" = 0.25
      ),
      guide = "none"
    ) +
    ggplot2::scale_x_continuous(
      breaks = c(
        -1,
        1
      ),
      labels = c(
        "mor < 0
repression",
        "mor > 0
activation"
      )
    ) +
    ggplot2::labs(
      x = "CollecTRI mode of regulation",
      y = "DESeq2 Wald statistic",
      tag = tag
    ) +
    ggplot2::theme_classic(
      base_size = 9
    ) +
    ggplot2::theme(
      plot.tag = ggplot2::element_text(
        face = "bold",
        size = 18
      ),
      plot.tag.position = c(
        0.01,
        0.99
      ),
      plot.margin = ggplot2::margin(
        5,
        5,
        5,
        5
      )
    )

  if (facet) {
    p <- p +
      ggplot2::facet_wrap(
        ~ celltype,
        scales = "free_y"
      )
  }

  p
}


make_jun_lollipop <- function(
  jun_target_df,
  celltype_focus,
  top_n = 15,
  tag = "C"
) {

  plot_df <- jun_target_df %>%
    dplyr::filter(
      celltype == celltype_focus
    ) %>%
    dplyr::arrange(
      dplyr::desc(
        abs(contribution)
      )
    ) %>%
    dplyr::slice_head(
      n = top_n
    ) %>%
    dplyr::mutate(
      gene = factor(
        gene,
        levels = rev(gene)
      ),
      regulation = dplyr::if_else(
        mor > 0,
        "Activation",
        "Repression"
      ),
      significant = !is.na(padj) & padj < 0.05
    )

  ggplot2::ggplot(
    plot_df,
    ggplot2::aes(
      x = contribution,
      y = gene
    )
  ) +
    ggplot2::geom_segment(
      ggplot2::aes(
        x = 0,
        xend = contribution,
        y = gene,
        yend = gene
      ),
      linewidth = 0.6,
      color = "grey60"
    ) +
    ggplot2::geom_point(
      ggplot2::aes(
        color = regulation,
        shape = significant
      ),
      size = 3.4,
      alpha = 0.95
    ) +
    ggplot2::scale_color_manual(
      values = c(
        "Activation" = "#B2182B",
        "Repression" = "#2166AC"
      ),
      name = "CollecTRI mor"
    ) +
    ggplot2::scale_shape_manual(
      values = c(
        "TRUE" = 19,
        "FALSE" = 1
      ),
      name = "DE padj < 0.05"
    ) +
    ggplot2::geom_vline(
      xintercept = 0,
      linetype = "dashed",
      color = "grey50",
      linewidth = 0.35
    ) +
    ggplot2::labs(
      x = "Signed contribution (Wald stat × mor)",
      y = NULL,
      tag = tag
    ) +
    ggplot2::theme_classic(
      base_size = 9
    ) +
    ggplot2::theme(
      plot.tag = ggplot2::element_text(
        face = "bold",
        size = 18
      ),
      plot.tag.position = c(
        0.01,
        0.99
      ),
      axis.text.y = ggplot2::element_text(
        face = "bold"
      ),
      plot.margin = ggplot2::margin(
        5,
        5,
        5,
        5
      )
    )
}
```

# Load data

```{r load-data}
if (!file.exists(SEURAT_RDS)) {
  stop(
    "Missing Seurat file: ",
    SEURAT_RDS
  )
}

if (!file.exists(TF_TABLE)) {
  stop(
    "Missing TF table: ",
    TF_TABLE
  )
}

if (!file.exists(DE_TABLE)) {
  stop(
    "Missing DESeq2 table: ",
    DE_TABLE
  )
}

seu <- readRDS(
  SEURAT_RDS
)

if (!inherits(seu, "Seurat")) {
  stop(
    "SEURAT_RDS does not contain a Seurat object."
  )
}

if (!CELLTYPE_COL %in% colnames(seu@meta.data)) {
  stop(
    "Column ",
    CELLTYPE_COL,
    " not found in Seurat metadata."
  )
}

tf_all <- read.delim(
  TF_TABLE,
  stringsAsFactors = FALSE,
  check.names = FALSE
) %>%
  dplyr::mutate(
    source = as.character(source),
    celltype = as.character(celltype),
    estimate = as.numeric(estimate),
    padj = as.numeric(padj)
  )

de_all <- read.delim(
  DE_TABLE,
  stringsAsFactors = FALSE,
  check.names = FALSE
) %>%
  dplyr::mutate(
    celltype = as.character(celltype),
    gene = as.character(gene),
    stat = as.numeric(stat),
    padj = as.numeric(padj)
  )

celltypes_present <- intersect(
  CELLTYPE_ORDER_REFERENCE,
  unique(tf_all$celltype)
)

celltypes_extra <- setdiff(
  unique(tf_all$celltype),
  celltypes_present
)

celltype_order <- c(
  celltypes_present,
  sort(celltypes_extra)
)

collectri <- load_collectri_static()

focus_net <- collectri %>%
  dplyr::filter(
    source == TF_FOCUS
  ) %>%
  dplyr::select(
    target,
    mor
  )

if (nrow(focus_net) == 0) {
  stop(
    "No targets found for ",
    TF_FOCUS,
    " in CollecTRI."
  )
}

tf_sel <- select_stratified_tfs(
  tf_all = tf_all,
  tf_focus = TF_FOCUS,
  top_n = TOP_N_TF,
  celltype_order = celltype_order
)

jun_info <- select_jun_targets(
  de_all = de_all,
  focus_net = focus_net,
  top_n = TOP_JUN_TARGETS,
  celltype_order = celltype_order
)

jun_target_df <- jun_info$jun_target_df
jun_target_rank <- jun_info$target_rank
top_jun_targets <- jun_info$top_targets

preferred_reductions <- c(
  "umap.rpca",
  "umap",
  "wnn.umap",
  "umap.unintegrated"
)

reduction_name <- preferred_reductions[
  preferred_reductions %in%
    names(
      seu@reductions
    )
][1]

if (
  length(reduction_name) == 0 ||
  is.na(reduction_name)
) {
  stop(
    "No compatible UMAP reduction found. Available: ",
    paste(
      names(
        seu@reductions
      ),
      collapse = ", "
    )
  )
}

jun_tf_table <- tf_all %>%
  dplyr::filter(
    source == TF_FOCUS,
    celltype %in% celltype_order
  ) %>%
  dplyr::arrange(
    padj,
    dplyr::desc(
      abs(estimate)
    )
  )

jun_best_celltype <- jun_tf_table %>%
  dplyr::slice_head(
    n = 1
  ) %>%
  dplyr::pull(
    celltype
  )

jun_top_celltypes <- jun_tf_table %>%
  dplyr::slice_head(
    n = min(
      3,
      nrow(jun_tf_table)
    )
  ) %>%
  dplyr::pull(
    celltype
  )

selection_table <- tf_sel %>%
  dplyr::select(
    source,
    representative_celltype = celltype,
    estimate,
    padj
  )

write.table(
  selection_table,
  file.path(
    OUTDIR,
    "selected_top10_tfs.tsv"
  ),
  sep = "\t",
  quote = FALSE,
  row.names = FALSE
)

write.table(
  top_jun_targets,
  file.path(
    OUTDIR,
    "selected_jun_targets.tsv"
  ),
  sep = "\t",
  quote = FALSE,
  row.names = FALSE
)
```

# Existing representation

```{r existing-figure, results='asis'}
if (file.exists(CURRENT_FIG_PNG)) {

  cat(
    "### Current ANR figure\n\n"
  )

  print(
    knitr::include_graphics(
      CURRENT_FIG_PNG
    )
  )

} else {

  cat(
    "Current combined figure not found at: ",
    CURRENT_FIG_PNG,
    "\n"
  )
}
```

# Panel A

```{r panel-a}
p_a <- make_umap(
  seu = seu,
  reduction_name = reduction_name,
  celltype_col = CELLTYPE_COL,
  celltype_order = celltype_order
)

save_plot(
  p_a,
  "panel_A_umap",
  width = 8,
  height = 6
)

p_a
```

# Alternative panel B representations {.tabset}

## B1 - Raw ULM heatmap

Closest to the current ANR representation. ULM scores retain their original
DMD-vs-CTRL sign and magnitude.

```{r b1}
p_b1 <- make_B_heatmap_raw(
  tf_all = tf_all,
  tf_sel = tf_sel,
  celltype_order = celltype_order,
  tag = "B"
)

save_plot(
  p_b1,
  "panel_B1_raw_heatmap",
  width = 10,
  height = 4.8
)

p_b1
```

## B2 - Row-scaled matrixplot-like heatmap

Inspired by matrix-style single-cell activity summaries. This emphasizes
relative cell-type specificity within each TF, rather than absolute ULM
magnitude.

```{r b2}
p_b2 <- make_B_heatmap_scaled(
  tf_all = tf_all,
  tf_sel = tf_sel,
  celltype_order = celltype_order,
  tag = "B"
)

save_plot(
  p_b2,
  "panel_B2_scaled_heatmap",
  width = 10,
  height = 4.8
)

p_b2
```

## B3 - Dotplot

Color encodes signed ULM activity and point size encodes adjusted significance.

```{r b3}
p_b3 <- make_B_dotplot(
  tf_all = tf_all,
  tf_sel = tf_sel,
  celltype_order = celltype_order,
  tag = "B"
)

save_plot(
  p_b3,
  "panel_B3_dotplot",
  width = 10,
  height = 4.8
)

p_b3
```

# Alternative panel C representations for JUN {.tabset}

## C1 - Source-target view: best JUN cell type

This follows the source-target logic used by decoupler: CollecTRI mode of
regulation on the x-axis and the signed DESeq2 Wald statistic on the y-axis.

```{r c1}
p_c1 <- make_source_targets_plot(
  jun_target_df = jun_target_df %>%
    dplyr::filter(
      gene %in%
        top_jun_targets$gene
    ),
  celltypes_use = jun_best_celltype,
  top_label_n = 12,
  facet = FALSE,
  tag = "C"
) +
  ggplot2::ggtitle(
    paste0(
      "JUN source-target view: ",
      jun_best_celltype
    )
  )

save_plot(
  p_c1,
  "panel_C1_source_targets_best_celltype",
  width = 7.5,
  height = 5.5
)

p_c1
```

## C2 - Source-target view: top three JUN cell types

Same representation, faceted over the three cell populations with the strongest
JUN evidence.

```{r c2}
p_c2 <- make_source_targets_plot(
  jun_target_df = jun_target_df %>%
    dplyr::filter(
      gene %in%
        top_jun_targets$gene
    ),
  celltypes_use = jun_top_celltypes,
  top_label_n = 8,
  facet = TRUE,
  tag = "C"
) +
  ggplot2::ggtitle(
    "JUN source-target view across top cell populations"
  )

save_plot(
  p_c2,
  "panel_C2_source_targets_top3_celltypes",
  width = 11,
  height = 6.5
)

p_c2
```

## C3 - Leading JUN targets

A compact lollipop view of the strongest target-level contributions in the
cell type with the strongest JUN evidence.

```{r c3}
p_c3 <- make_jun_lollipop(
  jun_target_df = jun_target_df,
  celltype_focus = jun_best_celltype,
  top_n = 15,
  tag = "C"
) +
  ggplot2::ggtitle(
    paste0(
      "Top JUN targets in ",
      jun_best_celltype
    )
  )

save_plot(
  p_c3,
  "panel_C3_jun_lollipop_best_celltype",
  width = 7.5,
  height = 5.5
)

p_c3
```

# Candidate combined figures {.tabset}

## Candidate 1 - A + raw heatmap + single source-target plot

```{r combo1}
combo1 <- p_a +
  (
    p_b1 /
      p_c1
  ) +
  patchwork::plot_layout(
    widths = c(
      1.05,
      1.35
    )
  )

save_plot(
  combo1,
  "candidate_figure_AB1C1",
  width = 15,
  height = 8
)

combo1
```

## Candidate 2 - A + scaled heatmap + multi-cell-type source-target plot

```{r combo2}
combo2 <- p_a +
  (
    p_b2 /
      p_c2
  ) +
  patchwork::plot_layout(
    widths = c(
      1.05,
      1.35
    )
  )

save_plot(
  combo2,
  "candidate_figure_AB2C2",
  width = 15,
  height = 8.5
)

combo2
```

## Candidate 3 - A + dotplot + JUN target lollipop

```{r combo3}
combo3 <- p_a +
  (
    p_b3 /
      p_c3
  ) +
  patchwork::plot_layout(
    widths = c(
      1.05,
      1.35
    )
  )

save_plot(
  combo3,
  "candidate_figure_AB3C3",
  width = 15,
  height = 8.5
)

combo3
```

# Selection tables

## TFs selected for panel B

```{r tf-selection-table}
selection_table
```

## JUN targets selected for panel C

```{r jun-target-table}
top_jun_targets
```

# Saved outputs

```{r outputs}
saved_files <- list.files(
  OUTDIR,
  recursive = TRUE,
  full.names = FALSE
)

data.frame(
  file = saved_files
)
```
