---
title: "ANR preliminary TF activity gallery"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: hide
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 6,
  dpi = 150
)
```

# Packages

```{r packages}
INSTALL_MISSING <- TRUE

cran_pkgs <- c(
  "Seurat",
  "dplyr",
  "ggplot2",
  "patchwork",
  "ggrepel",
  "tibble",
  "tidyr",
  "rmarkdown",
  "reticulate"
)

missing_cran <- cran_pkgs[
  !vapply(
    cran_pkgs,
    requireNamespace,
    logical(1),
    quietly = TRUE
  )
]

if (length(missing_cran) > 0) {
  if (!INSTALL_MISSING) {
    stop(
      "Missing packages: ",
      paste(missing_cran, collapse = ", ")
    )
  }

  install.packages(
    missing_cran,
    repos = "https://cloud.r-project.org"
  )
}

suppressPackageStartupMessages({
  library(Seurat)
  library(dplyr)
  library(ggplot2)
  library(patchwork)
  library(ggrepel)
  library(tibble)
  library(tidyr)
  library(reticulate)
})
```

# Configuration

```{r config}
SEURAT_RDS <- file.path(
  "data",
  "Integration_paravertebral_final.rds"
)

TF_TABLE <- file.path(
  "results_tf_activity",
  "TF_activity",
  "all_celltypes_CollecTRI_ULM.tsv"
)

DE_TABLE <- file.path(
  "results_tf_activity",
  "DESeq2",
  "all_celltypes_DMD_vs_CTRL.tsv"
)

CURRENT_FIG_PNG <- file.path(
  "results_tf_activity",
  "figures",
  "ANR_preliminary_snRNAseq_TF_activity.png"
)

OUTDIR <- file.path(
  "results_tf_activity",
  "figures",
  "anr_gallery"
)

dir.create(
  OUTDIR,
  recursive = TRUE,
  showWarnings = FALSE
)

TF_FOCUS <- "JUN"
TOP_N_TF <- 10
TOP_JUN_TARGETS <- 15
ACTIVITY_LIMIT <- 4

# Hybrid R/Python gallery. Python is resolved from the environment used to
# launch Rscript, keeping the report inside the active conda environment.
INSTALL_MISSING_PYTHON <- TRUE
PYTHON_DECOUPLER_SPEC <- "decoupler>=2.2.0"

CELLTYPE_COL <- "cell_type"
CONDITION_COL <- "condition"

CELLTYPE_ORDER_REFERENCE <- c(
  "Myofibers",
  "Regenerating Myofibers",
  "Satellite cells",
  "FAPs",
  "Immune cells",
  "Endothelial",
  "Smooth muscle",
  "Tenocytes",
  "Schwann cells",
  "Neural cells",
  "Adipocytes"
)

CELLTYPE_COLORS <- c(
  "Adipocytes" = "#E8B92E",
  "Endothelial" = "#6BAFB0",
  "FAPs" = "#4E79A7",
  "Immune cells" = "#F28E2B",
  "Myofibers" = "#D95F4E",
  "Neural cells" = "#7BC96F",
  "Regenerating Myofibers" = "#F08A84",
  "Satellite cells" = "#59A14F",
  "Schwann cells" = "#B07AA1",
  "Smooth muscle" = "#A96F9C",
  "Tenocytes" = "#9C755F"
)
```

# Helpers

```{r helpers}
save_plot <- function(
  plot,
  filename,
  width = 9,
  height = 6
) {

  png_path <- file.path(
    OUTDIR,
    paste0(
      filename,
      ".png"
    )
  )

  pdf_path <- file.path(
    OUTDIR,
    paste0(
      filename,
      ".pdf"
    )
  )

  svg_path <- file.path(
    OUTDIR,
    paste0(
      filename,
      ".svg"
    )
  )

  ggplot2::ggsave(
    filename = png_path,
    plot = plot,
    width = width,
    height = height,
    dpi = 300,
    bg = "white"
  )

  ggplot2::ggsave(
    filename = pdf_path,
    plot = plot,
    width = width,
    height = height,
    bg = "white"
  )

  # Use base R's SVG device to avoid an additional svglite/system dependency.
  grDevices::svg(
    filename = svg_path,
    width = width,
    height = height,
    bg = "white",
    onefile = TRUE
  )

  print(plot)
  grDevices::dev.off()

  invisible(
    c(
      png = png_path,
      pdf = pdf_path,
      svg = svg_path
    )
  )
}


figure_buttons <- function(
  filename,
  label = NULL
) {

  if (is.null(label)) {
    label <- filename
  }

  href_png <- file.path(
    OUTDIR,
    paste0(filename, ".png")
  )

  href_pdf <- file.path(
    OUTDIR,
    paste0(filename, ".pdf")
  )

  href_svg <- file.path(
    OUTDIR,
    paste0(filename, ".svg")
  )

  html <- paste0(
    "<div style='margin:8px 0 20px 0;display:flex;gap:8px;align-items:center;flex-wrap:wrap;'>",
    "<span style='font-weight:600;margin-right:4px;'>", label, "</span>",
    "<a href='", href_png, "' target='_blank' download ",
    "style='padding:6px 11px;background:#4D9221;color:white;text-decoration:none;border-radius:5px;'>PNG</a>",
    "<a href='", href_pdf, "' target='_blank' download ",
    "style='padding:6px 11px;background:#D95F02;color:white;text-decoration:none;border-radius:5px;'>PDF</a>",
    "<a href='", href_svg, "' target='_blank' download ",
    "style='padding:6px 11px;background:#2166AC;color:white;text-decoration:none;border-radius:5px;'>SVG</a>",
    "</div>"
  )

  knitr::asis_output(
    html
  )
}


load_collectri_static <- function(
  cache_dir = OUTDIR
) {

  collectri_url <- "https://rescued.omnipathdb.org/CollecTRI.csv"

  collectri_cache <- file.path(
    cache_dir,
    "CollecTRI_human.csv"
  )

  if (!file.exists(collectri_cache)) {

    message(
      "Downloading CollecTRI static network..."
    )

    utils::download.file(
      url = collectri_url,
      destfile = collectri_cache,
      mode = "wb",
      quiet = FALSE
    )
  }

  raw <- utils::read.csv(
    collectri_cache,
    stringsAsFactors = FALSE,
    check.names = FALSE
  )

  required_cols <- c(
    "source",
    "target",
    "weight"
  )

  missing_cols <- setdiff(
    required_cols,
    colnames(raw)
  )

  if (length(missing_cols) > 0) {
    stop(
      "Unexpected CollecTRI format. Missing columns: ",
      paste(
        missing_cols,
        collapse = ", "
      )
    )
  }

  raw %>%
    dplyr::transmute(
      source = as.character(source),
      target = as.character(target),
      mor = as.numeric(weight)
    ) %>%
    dplyr::filter(
      !is.na(source),
      !is.na(target),
      is.finite(mor),
      source != "",
      target != ""
    ) %>%
    dplyr::distinct(
      source,
      target,
      .keep_all = TRUE
    )
}


row_zscore <- function(x) {

  if (all(is.na(x))) {
    return(
      rep(
        NA_real_,
        length(x)
      )
    )
  }

  s <- stats::sd(
    x,
    na.rm = TRUE
  )

  m <- mean(
    x,
    na.rm = TRUE
  )

  if (
    !is.finite(s) ||
    s == 0
  ) {
    return(
      rep(
        0,
        length(x)
      )
    )
  }

  (x - m) / s
}


sig_stars <- function(p) {

  dplyr::case_when(
    is.na(p) ~ "",
    p < 0.001 ~ "***",
    p < 0.01 ~ "**",
    p < 0.05 ~ "*",
    TRUE ~ ""
  )
}


select_stratified_tfs <- function(
  tf_all,
  tf_focus = "JUN",
  top_n = 10,
  celltype_order
) {

  pair_rank <- tf_all %>%
    dplyr::filter(
      is.finite(estimate),
      !is.na(padj),
      padj < 0.05
    ) %>%
    dplyr::mutate(
      abs_activity = abs(estimate),
      celltype = as.character(celltype),
      source = as.character(source)
    ) %>%
    dplyr::group_by(celltype) %>%
    dplyr::arrange(
      padj,
      dplyr::desc(abs_activity),
      .by_group = TRUE
    ) %>%
    dplyr::mutate(
      cell_rank = dplyr::row_number()
    ) %>%
    dplyr::ungroup()

  focus_row <- pair_rank %>%
    dplyr::filter(
      source == tf_focus
    ) %>%
    dplyr::arrange(
      padj,
      dplyr::desc(abs_activity)
    ) %>%
    dplyr::slice_head(
      n = 1
    )

  if (nrow(focus_row) == 0) {

    focus_row <- tf_all %>%
      dplyr::filter(
        source == tf_focus,
        is.finite(estimate)
      ) %>%
      dplyr::mutate(
        abs_activity = abs(estimate),
        cell_rank = NA_integer_
      ) %>%
      dplyr::arrange(
        dplyr::desc(abs_activity)
      ) %>%
      dplyr::slice_head(
        n = 1
      )
  }

  if (nrow(focus_row) == 0) {
    stop(
      "Focus TF not found: ",
      tf_focus
    )
  }

  selected_rows <- focus_row

  selected_tfs <- unique(
    as.character(
      selected_rows$source
    )
  )

  covered_celltypes <- unique(
    as.character(
      selected_rows$celltype
    )
  )

  for (ct in celltype_order) {

    if (length(selected_tfs) >= top_n) {
      break
    }

    if (ct %in% covered_celltypes) {
      next
    }

    candidate <- pair_rank %>%
      dplyr::filter(
        celltype == ct,
        !source %in% selected_tfs
      ) %>%
      dplyr::slice_head(
        n = 1
      )

    if (nrow(candidate) == 0) {
      next
    }

    selected_rows <- dplyr::bind_rows(
      selected_rows,
      candidate
    )

    selected_tfs <- unique(
      c(
        selected_tfs,
        as.character(
          candidate$source
        )
      )
    )

    covered_celltypes <- unique(
      c(
        covered_celltypes,
        ct
      )
    )
  }

  if (length(selected_tfs) < top_n) {

    filler <- pair_rank %>%
      dplyr::filter(
        !source %in% selected_tfs
      ) %>%
      dplyr::arrange(
        cell_rank,
        padj,
        dplyr::desc(abs_activity)
      ) %>%
      dplyr::distinct(
        source,
        .keep_all = TRUE
      ) %>%
      dplyr::slice_head(
        n = top_n - length(selected_tfs)
      )

    selected_rows <- dplyr::bind_rows(
      selected_rows,
      filler
    )
  }

  selected_rows %>%
    dplyr::distinct(
      source,
      .keep_all = TRUE
    ) %>%
    dplyr::slice_head(
      n = top_n
    )
}


select_jun_targets <- function(
  de_all,
  focus_net,
  top_n = 15,
  celltype_order = NULL
) {

  jun_target_df <- de_all %>%
    dplyr::inner_join(
      focus_net,
      by = c(
        "gene" = "target"
      )
    ) %>%
    dplyr::filter(
      is.finite(stat),
      is.finite(mor)
    ) %>%
    dplyr::mutate(
      contribution = stat * mor,
      significant = !is.na(padj) & padj < 0.05,
      supportive = significant & contribution > 0
    )

  if (!is.null(celltype_order)) {

    jun_target_df <- jun_target_df %>%
      dplyr::filter(
        celltype %in% celltype_order
      )
  }

  target_rank <- jun_target_df %>%
    dplyr::group_by(gene) %>%
    dplyr::summarise(
      n_supportive = sum(
        supportive,
        na.rm = TRUE
      ),
      n_significant = sum(
        significant,
        na.rm = TRUE
      ),
      n_celltypes = dplyr::n_distinct(
        celltype[
          significant
        ]
      ),
      max_abs_contribution = max(
        abs(contribution),
        na.rm = TRUE
      ),
      mean_contribution = mean(
        contribution,
        na.rm = TRUE
      ),
      .groups = "drop"
    ) %>%
    dplyr::filter(
      n_supportive > 0
    ) %>%
    dplyr::arrange(
      dplyr::desc(n_supportive),
      dplyr::desc(n_celltypes),
      dplyr::desc(n_significant),
      dplyr::desc(max_abs_contribution),
      dplyr::desc(mean_contribution)
    )

  top_targets <- target_rank %>%
    dplyr::slice_head(
      n = top_n
    )

  list(
    jun_target_df = jun_target_df,
    target_rank = target_rank,
    top_targets = top_targets
  )
}


make_umap <- function(
  seu,
  reduction_name,
  celltype_col,
  celltype_order
) {

  emb <- as.data.frame(
    Seurat::Embeddings(
      seu,
      reduction = reduction_name
    )
  )

  colnames(emb)[1:2] <- c(
    "UMAP_1",
    "UMAP_2"
  )

  emb$celltype <- as.character(
    seu@meta.data[[celltype_col]]
  )

  plot_df <- emb %>%
    dplyr::filter(
      !is.na(celltype),
      celltype %in% celltype_order
    ) %>%
    dplyr::mutate(
      celltype = factor(
        celltype,
        levels = celltype_order
      )
    )

  ggplot2::ggplot(
    plot_df,
    ggplot2::aes(
      x = UMAP_1,
      y = UMAP_2,
      color = celltype
    )
  ) +
    ggplot2::geom_point(
      size = 0.16,
      alpha = 0.72,
      stroke = 0
    ) +
    ggplot2::scale_color_manual(
      values = CELLTYPE_COLORS,
      drop = FALSE,
      guide = ggplot2::guide_legend(
        override.aes = list(
          size = 4,
          alpha = 1
        )
      ),
      name = NULL
    ) +
    ggplot2::coord_equal() +
    ggplot2::labs(
      x = "UMAP 1",
      y = "UMAP 2",
      tag = "A"
    ) +
    ggplot2::theme_classic(
      base_size = 14
    ) +
    ggplot2::theme(
      plot.tag = ggplot2::element_text(
        face = "bold",
        size = 25
      ),
      plot.tag.position = c(
        0.01,
        0.99
      ),
      legend.position = "right",
      legend.text = ggplot2::element_text(
        size = 13
      ),
      axis.title = ggplot2::element_text(
        size = 15
      ),
      axis.text = ggplot2::element_blank(),
      axis.ticks = ggplot2::element_blank(),
      legend.title = ggplot2::element_text(
        size = 12
      ),
      legend.text = ggplot2::element_text(
        size = 11
      ),
      axis.title = ggplot2::element_text(
        size = 13
      ),
      plot.margin = ggplot2::margin(
        5,
        5,
        5,
        5
      )
    )
}


make_B_heatmap_raw <- function(
  tf_all,
  tf_sel,
  celltype_order,
  tag = "B"
) {

  top_tfs <- as.character(
    tf_sel$source
  )

  plot_df <- tf_all %>%
    dplyr::filter(
      source %in% top_tfs,
      celltype %in% celltype_order
    ) %>%
    dplyr::mutate(
      source = factor(
        source,
        levels = rev(top_tfs)
      ),
      celltype = factor(
        celltype,
        levels = celltype_order
      ),
      plot_estimate = pmax(
        -ACTIVITY_LIMIT,
        pmin(
          ACTIVITY_LIMIT,
          estimate
        )
      ),
      stars = sig_stars(
        padj
      )
    )

  ggplot2::ggplot(
    plot_df,
    ggplot2::aes(
      x = celltype,
      y = source,
      fill = plot_estimate
    )
  ) +
    ggplot2::geom_tile(
      color = "white",
      linewidth = 0.5
    ) +
    ggplot2::geom_text(
      ggplot2::aes(
        label = stars
      ),
      size = 5.0,
      fontface = "bold"
    ) +
    ggplot2::scale_fill_gradient2(
      low = "#2166AC",
      mid = "white",
      high = "#B2182B",
      midpoint = 0,
      limits = c(
        -ACTIVITY_LIMIT,
        ACTIVITY_LIMIT
      ),
      name = "ULM score"
    ) +
    ggplot2::labs(
      x = NULL,
      y = NULL,
      tag = tag
    ) +
    ggplot2::theme_minimal(
      base_size = 13
    ) +
    ggplot2::theme(
      plot.tag = ggplot2::element_text(
        face = "bold",
        size = 25
      ),
      plot.tag.position = c(
        0.01,
        0.99
      ),
      axis.text.x = ggplot2::element_text(
        angle = 38,
        hjust = 1,
        size = 12
      ),
      axis.text.y = ggplot2::element_text(
        face = "bold",
        size = 13
      ),
      panel.grid = ggplot2::element_blank(),
      legend.title = ggplot2::element_text(
        size = 12
      ),
      legend.text = ggplot2::element_text(
        size = 11
      ),
      axis.title = ggplot2::element_text(
        size = 13
      ),
      plot.margin = ggplot2::margin(
        5,
        5,
        5,
        5
      )
    )
}


make_B_heatmap_scaled <- function(
  tf_all,
  tf_sel,
  celltype_order,
  tag = "B"
) {

  top_tfs <- as.character(
    tf_sel$source
  )

  plot_df <- tf_all %>%
    dplyr::filter(
      source %in% top_tfs,
      celltype %in% celltype_order
    ) %>%
    dplyr::group_by(source) %>%
    dplyr::mutate(
      scaled_estimate = row_zscore(
        estimate
      )
    ) %>%
    dplyr::ungroup() %>%
    dplyr::mutate(
      source = factor(
        source,
        levels = rev(top_tfs)
      ),
      celltype = factor(
        celltype,
        levels = celltype_order
      ),
      stars = sig_stars(
        padj
      )
    )

  ggplot2::ggplot(
    plot_df,
    ggplot2::aes(
      x = celltype,
      y = source,
      fill = scaled_estimate
    )
  ) +
    ggplot2::geom_tile(
      color = "white",
      linewidth = 0.5
    ) +
    ggplot2::geom_text(
      ggplot2::aes(
        label = stars
      ),
      size = 5.0,
      fontface = "bold"
    ) +
    ggplot2::scale_fill_gradient2(
      low = "#2166AC",
      mid = "white",
      high = "#B2182B",
      midpoint = 0,
      limits = c(
        -2.5,
        2.5
      ),
      name = "Row-scaled
ULM score"
    ) +
    ggplot2::labs(
      x = NULL,
      y = NULL,
      tag = tag
    ) +
    ggplot2::theme_minimal(
      base_size = 13
    ) +
    ggplot2::theme(
      plot.tag = ggplot2::element_text(
        face = "bold",
        size = 25
      ),
      plot.tag.position = c(
        0.01,
        0.99
      ),
      axis.text.x = ggplot2::element_text(
        angle = 38,
        hjust = 1,
        size = 12
      ),
      axis.text.y = ggplot2::element_text(
        face = "bold",
        size = 13
      ),
      panel.grid = ggplot2::element_blank(),
      legend.title = ggplot2::element_text(
        size = 12
      ),
      legend.text = ggplot2::element_text(
        size = 11
      ),
      axis.title = ggplot2::element_text(
        size = 13
      ),
      plot.margin = ggplot2::margin(
        5,
        5,
        5,
        5
      )
    )
}


make_B_dotplot <- function(
  tf_all,
  tf_sel,
  celltype_order,
  tag = "B"
) {

  top_tfs <- as.character(
    tf_sel$source
  )

  plot_df <- tf_all %>%
    dplyr::filter(
      source %in% top_tfs,
      celltype %in% celltype_order
    ) %>%
    dplyr::mutate(
      source = factor(
        source,
        levels = rev(top_tfs)
      ),
      celltype = factor(
        celltype,
        levels = celltype_order
      ),
      neglog10_padj = dplyr::if_else(
        is.na(padj),
        0,
        pmin(
          10,
          -log10(
            padj + 1e-300
          )
        )
      ),
      plot_estimate = pmax(
        -ACTIVITY_LIMIT,
        pmin(
          ACTIVITY_LIMIT,
          estimate
        )
      )
    )

  ggplot2::ggplot(
    plot_df,
    ggplot2::aes(
      x = celltype,
      y = source
    )
  ) +
    ggplot2::geom_point(
      ggplot2::aes(
        size = neglog10_padj,
        color = plot_estimate
      ),
      alpha = 0.95
    ) +
    ggplot2::scale_color_gradient2(
      low = "#2166AC",
      mid = "white",
      high = "#B2182B",
      midpoint = 0,
      limits = c(
        -ACTIVITY_LIMIT,
        ACTIVITY_LIMIT
      ),
      name = "ULM score"
    ) +
    ggplot2::scale_size_continuous(
      name = "-log10(padj)",
      range = c(
        1,
        8
      )
    ) +
    ggplot2::labs(
      x = NULL,
      y = NULL,
      tag = tag
    ) +
    ggplot2::theme_minimal(
      base_size = 13
    ) +
    ggplot2::theme(
      plot.tag = ggplot2::element_text(
        face = "bold",
        size = 25
      ),
      plot.tag.position = c(
        0.01,
        0.99
      ),
      axis.text.x = ggplot2::element_text(
        angle = 38,
        hjust = 1,
        size = 12
      ),
      axis.text.y = ggplot2::element_text(
        face = "bold",
        size = 13
      ),
      panel.grid.minor = ggplot2::element_blank(),
      legend.title = ggplot2::element_text(
        size = 12
      ),
      legend.text = ggplot2::element_text(
        size = 11
      ),
      axis.title = ggplot2::element_text(
        size = 13
      ),
      plot.margin = ggplot2::margin(
        5,
        5,
        5,
        5
      )
    )
}


make_source_targets_plot <- function(
  jun_target_df,
  celltypes_use,
  top_label_n = 12,
  facet = TRUE,
  tag = "C"
) {

  plot_df <- jun_target_df %>%
    dplyr::filter(
      celltype %in% celltypes_use
    ) %>%
    dplyr::group_by(celltype) %>%
    dplyr::arrange(
      gene,
      .by_group = TRUE
    ) %>%
    dplyr::mutate(
      jitter_index = dplyr::row_number(),
      x_jitter = mor +
        (
          (
            jitter_index %% 9
          ) - 4
        ) * 0.025,
      sig = !is.na(padj) & padj < 0.05
    ) %>%
    dplyr::ungroup()

  label_df <- plot_df %>%
    dplyr::group_by(celltype) %>%
    dplyr::arrange(
      dplyr::desc(
        abs(contribution)
      ),
      .by_group = TRUE
    ) %>%
    dplyr::slice_head(
      n = top_label_n
    ) %>%
    dplyr::ungroup()

  p <- ggplot2::ggplot(
    plot_df,
    ggplot2::aes(
      x = x_jitter,
      y = stat
    )
  ) +
    ggplot2::geom_vline(
      xintercept = 0,
      linetype = "dashed",
      color = "grey55",
      linewidth = 0.35
    ) +
    ggplot2::geom_hline(
      yintercept = 0,
      linetype = "dashed",
      color = "grey55",
      linewidth = 0.35
    ) +
    ggplot2::geom_point(
      ggplot2::aes(
        fill = contribution,
        alpha = sig
      ),
      shape = 21,
      size = 2.6,
      color = "black",
      stroke = 0.2
    ) +
    ggrepel::geom_text_repel(
      data = label_df,
      ggplot2::aes(
        label = gene
      ),
      size = 4.0,
      box.padding = 0.25,
      point.padding = 0.15,
      max.overlaps = Inf,
      seed = 1
    ) +
    ggplot2::scale_fill_gradient2(
      low = "#2166AC",
      mid = "white",
      high = "#B2182B",
      midpoint = 0,
      name = "stat × mor"
    ) +
    ggplot2::scale_alpha_manual(
      values = c(
        "TRUE" = 0.95,
        "FALSE" = 0.25
      ),
      guide = "none"
    ) +
    ggplot2::scale_x_continuous(
      breaks = c(
        -1,
        1
      ),
      labels = c(
        "mor < 0
repression",
        "mor > 0
activation"
      )
    ) +
    ggplot2::labs(
      x = "CollecTRI mode of regulation",
      y = "DESeq2 Wald statistic",
      tag = tag
    ) +
    ggplot2::theme_classic(
      base_size = 13
    ) +
    ggplot2::theme(
      plot.tag = ggplot2::element_text(
        face = "bold",
        size = 25
      ),
      plot.tag.position = c(
        0.01,
        0.99
      ),
      legend.title = ggplot2::element_text(
        size = 12
      ),
      legend.text = ggplot2::element_text(
        size = 11
      ),
      axis.title = ggplot2::element_text(
        size = 13
      ),
      plot.margin = ggplot2::margin(
        5,
        5,
        5,
        5
      )
    )

  if (facet) {
    p <- p +
      ggplot2::facet_wrap(
        ~ celltype,
        scales = "free_y"
      )
  }

  p
}


make_jun_lollipop <- function(
  jun_target_df,
  celltype_focus,
  top_n = 15,
  tag = "C"
) {

  plot_df <- jun_target_df %>%
    dplyr::filter(
      celltype == celltype_focus
    ) %>%
    dplyr::arrange(
      dplyr::desc(
        abs(contribution)
      )
    ) %>%
    dplyr::slice_head(
      n = top_n
    ) %>%
    dplyr::mutate(
      gene = factor(
        gene,
        levels = rev(gene)
      ),
      regulation = dplyr::if_else(
        mor > 0,
        "Activation",
        "Repression"
      ),
      significant = !is.na(padj) & padj < 0.05
    )

  ggplot2::ggplot(
    plot_df,
    ggplot2::aes(
      x = contribution,
      y = gene
    )
  ) +
    ggplot2::geom_segment(
      ggplot2::aes(
        x = 0,
        xend = contribution,
        y = gene,
        yend = gene
      ),
      linewidth = 0.6,
      color = "grey60"
    ) +
    ggplot2::geom_point(
      ggplot2::aes(
        color = regulation,
        shape = significant
      ),
      size = 3.4,
      alpha = 0.95
    ) +
    ggplot2::scale_color_manual(
      values = c(
        "Activation" = "#B2182B",
        "Repression" = "#2166AC"
      ),
      name = "CollecTRI mor"
    ) +
    ggplot2::scale_shape_manual(
      values = c(
        "TRUE" = 19,
        "FALSE" = 1
      ),
      name = "DE padj < 0.05"
    ) +
    ggplot2::geom_vline(
      xintercept = 0,
      linetype = "dashed",
      color = "grey50",
      linewidth = 0.35
    ) +
    ggplot2::labs(
      x = "Signed contribution (Wald stat × mor)",
      y = NULL,
      tag = tag
    ) +
    ggplot2::theme_classic(
      base_size = 13
    ) +
    ggplot2::theme(
      plot.tag = ggplot2::element_text(
        face = "bold",
        size = 25
      ),
      plot.tag.position = c(
        0.01,
        0.99
      ),
      axis.text.y = ggplot2::element_text(
        face = "bold",
        size = 13
      ),
      legend.title = ggplot2::element_text(
        size = 12
      ),
      legend.text = ggplot2::element_text(
        size = 11
      ),
      axis.title = ggplot2::element_text(
        size = 13
      ),
      plot.margin = ggplot2::margin(
        5,
        5,
        5,
        5
      )
    )
}
```

# Load data

```{r load-data}
if (!file.exists(SEURAT_RDS)) {
  stop(
    "Missing Seurat file: ",
    SEURAT_RDS
  )
}

if (!file.exists(TF_TABLE)) {
  stop(
    "Missing TF table: ",
    TF_TABLE
  )
}

if (!file.exists(DE_TABLE)) {
  stop(
    "Missing DESeq2 table: ",
    DE_TABLE
  )
}

seu <- readRDS(
  SEURAT_RDS
)

if (!inherits(seu, "Seurat")) {
  stop(
    "SEURAT_RDS does not contain a Seurat object."
  )
}

if (!CELLTYPE_COL %in% colnames(seu@meta.data)) {
  stop(
    "Column ",
    CELLTYPE_COL,
    " not found in Seurat metadata."
  )
}

tf_all <- read.delim(
  TF_TABLE,
  stringsAsFactors = FALSE,
  check.names = FALSE
) %>%
  dplyr::mutate(
    source = as.character(source),
    celltype = as.character(celltype),
    estimate = as.numeric(estimate),
    padj = as.numeric(padj)
  )

de_all <- read.delim(
  DE_TABLE,
  stringsAsFactors = FALSE,
  check.names = FALSE
) %>%
  dplyr::mutate(
    celltype = as.character(celltype),
    gene = as.character(gene),
    stat = as.numeric(stat),
    padj = as.numeric(padj)
  )

celltypes_present <- intersect(
  CELLTYPE_ORDER_REFERENCE,
  unique(tf_all$celltype)
)

celltypes_extra <- setdiff(
  unique(tf_all$celltype),
  celltypes_present
)

celltype_order <- c(
  celltypes_present,
  sort(celltypes_extra)
)

collectri <- load_collectri_static()

focus_net <- collectri %>%
  dplyr::filter(
    source == TF_FOCUS
  ) %>%
  dplyr::select(
    target,
    mor
  )

if (nrow(focus_net) == 0) {
  stop(
    "No targets found for ",
    TF_FOCUS,
    " in CollecTRI."
  )
}

tf_sel <- select_stratified_tfs(
  tf_all = tf_all,
  tf_focus = TF_FOCUS,
  top_n = TOP_N_TF,
  celltype_order = celltype_order
)

jun_info <- select_jun_targets(
  de_all = de_all,
  focus_net = focus_net,
  top_n = TOP_JUN_TARGETS,
  celltype_order = celltype_order
)

jun_target_df <- jun_info$jun_target_df
jun_target_rank <- jun_info$target_rank
top_jun_targets <- jun_info$top_targets

preferred_reductions <- c(
  "umap.rpca",
  "umap",
  "wnn.umap",
  "umap.unintegrated"
)

reduction_name <- preferred_reductions[
  preferred_reductions %in%
    names(
      seu@reductions
    )
][1]

if (
  length(reduction_name) == 0 ||
  is.na(reduction_name)
) {
  stop(
    "No compatible UMAP reduction found. Available: ",
    paste(
      names(
        seu@reductions
      ),
      collapse = ", "
    )
  )
}

jun_tf_table <- tf_all %>%
  dplyr::filter(
    source == TF_FOCUS,
    celltype %in% celltype_order
  ) %>%
  dplyr::arrange(
    padj,
    dplyr::desc(
      abs(estimate)
    )
  )

jun_best_celltype <- jun_tf_table %>%
  dplyr::slice_head(
    n = 1
  ) %>%
  dplyr::pull(
    celltype
  )

jun_top_celltypes <- jun_tf_table %>%
  dplyr::slice_head(
    n = min(
      3,
      nrow(jun_tf_table)
    )
  ) %>%
  dplyr::pull(
    celltype
  )

selection_table <- tf_sel %>%
  dplyr::select(
    source,
    representative_celltype = celltype,
    estimate,
    padj
  )

write.table(
  selection_table,
  file.path(
    OUTDIR,
    "selected_top10_tfs.tsv"
  ),
  sep = "\t",
  quote = FALSE,
  row.names = FALSE
)

write.table(
  top_jun_targets,
  file.path(
    OUTDIR,
    "selected_jun_targets.tsv"
  ),
  sep = "\t",
  quote = FALSE,
  row.names = FALSE
)

# Small bridge files for native Python/decoupler plots. The donor-aware
# pseudobulk and DESeq2 statistics are computed in R and passed unchanged.
python_tf_path <- file.path(OUTDIR, "python_tf_activity.tsv")
python_de_path <- file.path(OUTDIR, "python_de_stats.tsv")
python_net_path <- file.path(OUTDIR, "python_JUN_collectri.tsv")
python_context_path <- file.path(OUTDIR, "python_context.tsv")

write.table(
  tf_all,
  python_tf_path,
  sep = "\t",
  quote = FALSE,
  row.names = FALSE
)

write.table(
  de_all,
  python_de_path,
  sep = "\t",
  quote = FALSE,
  row.names = FALSE
)

python_net <- focus_net %>%
  dplyr::transmute(
    source = TF_FOCUS,
    target = as.character(target),
    weight = as.numeric(mor)
  )

write.table(
  python_net,
  python_net_path,
  sep = "\t",
  quote = FALSE,
  row.names = FALSE
)

python_context <- data.frame(
  key = c(
    "focus_tf",
    "best_celltype",
    "top_celltypes",
    "outdir"
  ),
  value = c(
    TF_FOCUS,
    jun_best_celltype,
    paste(jun_top_celltypes, collapse = "||"),
    OUTDIR
  ),
  stringsAsFactors = FALSE
)

write.table(
  python_context,
  python_context_path,
  sep = "\t",
  quote = FALSE,
  row.names = FALSE
)
```

# Python / decoupler bridge

The following native panels are generated by the current Python implementation
of `decoupler`. R remains responsible for the Seurat object, donor-aware
pseudobulk statistics and DESeq2 results; Python receives those tables and is
used only for the official decoupler plotting functions.

```{r python-runtime}
python_bin <- Sys.which("python")

if (!nzchar(python_bin)) {
  stop(
    "No Python executable found in PATH. Activate the conda environment before rendering."
  )
}

required_python_modules <- c(
  "decoupler",
  "pandas",
  "numpy",
  "matplotlib",
  "igraph"
)

python_module_list <- paste0(
  "[",
  paste(
    shQuote(
      required_python_modules,
      type = "cmd"
    ),
    collapse = ","
  ),
  "]"
)

# Build a valid Python list explicitly; do not rely on non-base-R helpers.
check_code <- paste0(
  "import importlib.util,sys; mods=",
  python_module_list,
  "; sys.exit(0 if all(importlib.util.find_spec(m) is not None for m in mods) else 1)"
)

py_status <- suppressWarnings(
  system2(
    python_bin,
    c("-c", shQuote(check_code))
  )
)

if (!identical(py_status, 0L)) {
  if (!INSTALL_MISSING_PYTHON) {
    stop(
      "Missing Python modules: decoupler, pandas, numpy, matplotlib and/or igraph."
    )
  }

  message(
    "Installing Python dependencies into: ",
    python_bin
  )

  install_status <- system2(
    python_bin,
    c(
      "-m",
      "pip",
      "install",
      shQuote(
        PYTHON_DECOUPLER_SPEC
      ),
      "pandas",
      "numpy",
      "matplotlib",
      "igraph"
    )
  )

  if (!identical(install_status, 0L)) {
    stop(
      "Python dependency installation failed. ",
      "Run python -m pip install '",
      PYTHON_DECOUPLER_SPEC,
      "' pandas numpy matplotlib igraph"
    )
  }
}

reticulate::use_python(
  python_bin,
  required = TRUE
)

reticulate::py_config()
```

```{python python-imports}
from pathlib import Path
import re
import sys

import numpy as np
import pandas as pd
import matplotlib.pyplot as plt
import decoupler as dc

plt.rcParams.update({
    "font.size": 13,
    "axes.titlesize": 16,
    "axes.labelsize": 14,
    "xtick.labelsize": 12,
    "ytick.labelsize": 12,
    "legend.fontsize": 11,
    "legend.title_fontsize": 12,
})

base = Path("results_tf_activity") / "figures" / "anr_gallery"

tf = pd.read_csv(base / "python_tf_activity.tsv", sep="\t")
de = pd.read_csv(base / "python_de_stats.tsv", sep="\t")
net = pd.read_csv(base / "python_JUN_collectri.tsv", sep="\t")

ctx_df = pd.read_csv(base / "python_context.tsv", sep="\t")
ctx = dict(zip(ctx_df["key"], ctx_df["value"]))

focus_tf = ctx["focus_tf"]
best_celltype = ctx["best_celltype"]
top_celltypes = ctx["top_celltypes"].split("||")
outdir = Path(ctx["outdir"])
outdir.mkdir(parents=True, exist_ok=True)

def safe_name(x):
    return re.sub(r"[^A-Za-z0-9._-]+", "_", str(x))

def save_native(fig, stem):
    png = outdir / f"{stem}.png"
    pdf = outdir / f"{stem}.pdf"
    svg = outdir / f"{stem}.svg"
    fig.savefig(png, dpi=300, bbox_inches="tight", facecolor="white")
    fig.savefig(pdf, bbox_inches="tight", facecolor="white")
    fig.savefig(svg, bbox_inches="tight", facecolor="white", format="svg")
    return png, pdf, svg

print("Python:", sys.version.split()[0])
print("decoupler:", dc.__version__)
print(
    "Native plotting:",
    "source_targets=", hasattr(dc.pl, "source_targets"),
    "dotplot=", hasattr(dc.pl, "dotplot"),
    "network=", hasattr(dc.pl, "network"),
)
```

# Existing representation

```{r existing-figure, results='asis'}
if (file.exists(CURRENT_FIG_PNG)) {

  cat(
    "### Current ANR figure\n\n"
  )

  print(
    knitr::include_graphics(
      CURRENT_FIG_PNG
    )
  )

} else {

  cat(
    "Current combined figure not found at: ",
    CURRENT_FIG_PNG,
    "\n"
  )
}
```

# Panel A

```{r panel-a}
p_a <- make_umap(
  seu = seu,
  reduction_name = reduction_name,
  celltype_col = CELLTYPE_COL,
  celltype_order = celltype_order
)

save_plot(
  p_a,
  "panel_A_umap",
  width = 11,
  height = 8
)

p_a
```

```{r panel-a-downloads, echo=FALSE, results='asis'}
figure_buttons(
  "panel_A_umap",
  "Panel A"
)
```

# Alternative panel B representations {.tabset}

## B1 - Raw ULM heatmap

Closest to the current ANR representation. ULM scores retain their original
DMD-vs-CTRL sign and magnitude.

```{r b1}
p_b1 <- make_B_heatmap_raw(
  tf_all = tf_all,
  tf_sel = tf_sel,
  celltype_order = celltype_order,
  tag = "B"
)

save_plot(
  p_b1,
  "panel_B1_raw_heatmap",
  width = 12,
  height = 6.5
)

p_b1
```

```{r b1-downloads, echo=FALSE, results='asis'}
figure_buttons(
  "panel_B1_raw_heatmap",
  "Panel B1"
)
```

## B2 - Row-scaled matrixplot-like heatmap

Inspired by matrix-style single-cell activity summaries. This emphasizes
relative cell-type specificity within each TF, rather than absolute ULM
magnitude.

```{r b2}
p_b2 <- make_B_heatmap_scaled(
  tf_all = tf_all,
  tf_sel = tf_sel,
  celltype_order = celltype_order,
  tag = "B"
)

save_plot(
  p_b2,
  "panel_B2_scaled_heatmap",
  width = 12,
  height = 6.5
)

p_b2
```

```{r b2-downloads, echo=FALSE, results='asis'}
figure_buttons(
  "panel_B2_scaled_heatmap",
  "Panel B2"
)
```

## B3 - Dotplot

Color encodes signed ULM activity and point size encodes adjusted significance.

```{r b3}
p_b3 <- make_B_dotplot(
  tf_all = tf_all,
  tf_sel = tf_sel,
  celltype_order = celltype_order,
  tag = "B"
)

save_plot(
  p_b3,
  "panel_B3_dotplot",
  width = 12,
  height = 6.5
)

p_b3
```

```{r b3-downloads, echo=FALSE, results='asis'}
figure_buttons(
  "panel_B3_dotplot",
  "Panel B3"
)
```

# Alternative panel C representations for JUN {.tabset}

## C1 - Source-target view: best JUN cell type

This follows the source-target logic used by decoupler: CollecTRI mode of
regulation on the x-axis and the signed DESeq2 Wald statistic on the y-axis.

```{r c1}
p_c1 <- make_source_targets_plot(
  jun_target_df = jun_target_df %>%
    dplyr::filter(
      gene %in%
        top_jun_targets$gene
    ),
  celltypes_use = jun_best_celltype,
  top_label_n = 12,
  facet = FALSE,
  tag = "C"
) +
  ggplot2::ggtitle(
    paste0(
      "JUN source-target view: ",
      jun_best_celltype
    )
  )

save_plot(
  p_c1,
  "panel_C1_source_targets_best_celltype",
  width = 9,
  height = 7
)

p_c1
```

```{r c1-downloads, echo=FALSE, results='asis'}
figure_buttons(
  "panel_C1_source_targets_best_celltype",
  "Panel C1"
)
```

## C2 - Source-target view: top three JUN cell types

Same representation, faceted over the three cell populations with the strongest
JUN evidence.

```{r c2}
p_c2 <- make_source_targets_plot(
  jun_target_df = jun_target_df %>%
    dplyr::filter(
      gene %in%
        top_jun_targets$gene
    ),
  celltypes_use = jun_top_celltypes,
  top_label_n = 8,
  facet = TRUE,
  tag = "C"
) +
  ggplot2::ggtitle(
    "JUN source-target view across top cell populations"
  )

save_plot(
  p_c2,
  "panel_C2_source_targets_top3_celltypes",
  width = 13,
  height = 8
)

p_c2
```

```{r c2-downloads, echo=FALSE, results='asis'}
figure_buttons(
  "panel_C2_source_targets_top3_celltypes",
  "Panel C2"
)
```

## C3 - Leading JUN targets

A compact lollipop view of the strongest target-level contributions in the
cell type with the strongest JUN evidence.

```{r c3}
p_c3 <- make_jun_lollipop(
  jun_target_df = jun_target_df,
  celltype_focus = jun_best_celltype,
  top_n = 15,
  tag = "C"
) +
  ggplot2::ggtitle(
    paste0(
      "Top JUN targets in ",
      jun_best_celltype
    )
  )

save_plot(
  p_c3,
  "panel_C3_jun_lollipop_best_celltype",
  width = 9,
  height = 7
)

p_c3
```

```{r c3-downloads, echo=FALSE, results='asis'}
figure_buttons(
  "panel_C3_jun_lollipop_best_celltype",
  "Panel C3"
)
```

# Native Python / decoupler representations {.tabset}

These panels call the plotting functions from the scverse Python `decoupler`
package directly. They are additional comparisons; the underlying statistics
are the same donor-aware R results used above.

## B4 - Native decoupler dotplot

The native `decoupler.pl.dotplot` is shown for the cell population with the
strongest JUN evidence. Color is the ULM score and point size is
`-log10(BH-adjusted p)`.

```{python b4-python-native-dotplot}
b4 = tf.loc[
    (tf["celltype"] == best_celltype)
    & pd.to_numeric(tf["estimate"], errors="coerce").notna()
].copy()

b4["estimate"] = pd.to_numeric(b4["estimate"], errors="coerce")
b4["padj"] = pd.to_numeric(b4["padj"], errors="coerce")
b4["neglog10_padj"] = -np.log10(
    b4["padj"].clip(lower=np.finfo(float).tiny, upper=1.0)
)

fig_b4 = dc.pl.dotplot(
    df=b4,
    x="estimate",
    y="source",
    c="estimate",
    s="neglog10_padj",
    top=10,
    scale=0.22,
    cmap="RdBu_r",
    vcenter=0,
    return_fig=True,
    figsize=(8.5, 6.5),
)

fig_b4.axes[0].set_title(
    f"Native decoupler TF activity — {best_celltype}"
)
fig_b4.axes[0].set_xlabel("ULM score (DMD vs CTRL)")

save_native(
    fig_b4,
    "panel_B4_python_decoupler_dotplot_best_celltype",
)

plt.show()
```

```{r b4-downloads, echo=FALSE, results='asis'}
figure_buttons(
  "panel_B4_python_decoupler_dotplot_best_celltype",
  "Panel B4 (native Python)"
)
```

## C4 - Native decoupler source-target plot

This is `decoupler.pl.source_targets` itself. The x-axis is the CollecTRI
interaction weight (mode of regulation) and the y-axis is the DESeq2 Wald
statistic. Concordant quadrants are colored as positive support by decoupler.

```{python c4-python-source-targets}
de_best = de.loc[
    de["celltype"] == best_celltype
].copy()

de_best["stat"] = pd.to_numeric(
    de_best["stat"],
    errors="coerce",
)

de_best = (
    de_best
    .dropna(subset=["gene", "stat"])
    .drop_duplicates(subset=["gene"])
    .set_index("gene")
)

fig_c4 = dc.pl.source_targets(
    data=de_best,
    net=net,
    x="weight",
    y="stat",
    name=focus_tf,
    top=15,
    color_pos="#B2182B",
    color_neg="#2166AC",
    return_fig=True,
    figsize=(8.5, 6.8),
)

fig_c4.axes[0].set_title(
    f"{focus_tf} targets — {best_celltype}"
)
fig_c4.axes[0].set_xlabel(
    "CollecTRI weight / mode of regulation"
)
fig_c4.axes[0].set_ylabel(
    "DESeq2 Wald statistic (DMD vs CTRL)"
)

save_native(
    fig_c4,
    "panel_C4_python_decoupler_source_targets_best_celltype",
)

plt.show()
```

```{r c4-downloads, echo=FALSE, results='asis'}
figure_buttons(
  "panel_C4_python_decoupler_source_targets_best_celltype",
  "Panel C4 (native Python)"
)
```

## C5 - Native source-target plots across the top JUN populations

Each panel below is independently generated by the native decoupler function.

```{python c5-python-source-targets-top3}
for ct in top_celltypes:
    dct = de.loc[
        de["celltype"] == ct
    ].copy()

    dct["stat"] = pd.to_numeric(
        dct["stat"],
        errors="coerce",
    )

    dct = (
        dct
        .dropna(subset=["gene", "stat"])
        .drop_duplicates(subset=["gene"])
        .set_index("gene")
    )

    fig = dc.pl.source_targets(
        data=dct,
        net=net,
        x="weight",
        y="stat",
        name=focus_tf,
        top=12,
        color_pos="#B2182B",
        color_neg="#2166AC",
        return_fig=True,
        figsize=(8.0, 6.2),
    )

    fig.axes[0].set_title(
        f"{focus_tf} targets — {ct}"
    )
    fig.axes[0].set_xlabel(
        "CollecTRI weight / mode of regulation"
    )
    fig.axes[0].set_ylabel(
        "DESeq2 Wald statistic"
    )

    save_native(
        fig,
        "panel_C5_python_decoupler_source_targets_" + safe_name(ct),
    )

    plt.show()
    plt.close(fig)
```

```{r c5-downloads, echo=FALSE, results='asis'}
for (ct in jun_top_celltypes) {
  figure_buttons(
    paste0(
      "panel_C5_python_decoupler_source_targets_",
      gsub(
        "[^A-Za-z0-9._-]+",
        "_",
        ct
      )
    ),
    paste0(
      "Panel C5 - ",
      ct
    )
  )
}
```

## C6 - Native decoupler network with CollecTRI weights

This uses `decoupler.pl.network` directly. Positive and negative edge colors
are therefore assigned from the CollecTRI weights by decoupler itself. Target
node color is the DESeq2 Wald statistic and the JUN source node is colored by
its ULM activity score.

```{python c6-python-network}
target_stats = (
    de.loc[
        de["celltype"] == best_celltype,
        ["gene", "stat"],
    ]
    .dropna()
    .drop_duplicates(subset=["gene"])
)

target_stats["stat"] = pd.to_numeric(
    target_stats["stat"],
    errors="coerce",
)
target_stats = target_stats.dropna(subset=["stat"])

data_wide = pd.DataFrame(
    [
        dict(
            zip(
                target_stats["gene"],
                target_stats["stat"],
            )
        )
    ],
    index=[best_celltype],
)

jun_row = tf.loc[
    (tf["celltype"] == best_celltype)
    & (tf["source"] == focus_tf),
    "estimate",
]

if jun_row.empty:
    raise RuntimeError(
        f"No {focus_tf} activity score found for {best_celltype}"
    )

score_wide = pd.DataFrame(
    [[float(jun_row.iloc[0])]],
    index=[best_celltype],
    columns=[focus_tf],
)

fig_c6 = dc.pl.network(
    net=net,
    data=data_wide,
    score=score_wide,
    sources=focus_tf,
    targets=12,
    by_abs=True,
    size_node=6,
    size_label=2.8,
    s_cmap="RdBu_r",
    t_cmap="RdBu_r",
    vcenter=True,
    c_pos_w="#B2182B",
    c_neg_w="#2166AC",
    s_label="JUN ULM score",
    t_label="DESeq2 Wald statistic",
    layout="kk",
    return_fig=True,
    figsize=(9.0, 7.5),
)

fig_c6.suptitle(
    f"Native decoupler network — {best_celltype}",
    y=0.98,
)

save_native(
    fig_c6,
    "panel_C6_python_decoupler_network_best_celltype",
)

plt.show()
```

```{r c6-downloads, echo=FALSE, results='asis'}
figure_buttons(
  "panel_C6_python_decoupler_network_best_celltype",
  "Panel C6 (native Python)"
)
```

# Candidate combined figures {.tabset}

## Candidate 1 - A + raw heatmap + single source-target plot

```{r combo1}
combo1 <- p_a +
  (
    p_b1 /
      p_c1
  ) +
  patchwork::plot_layout(
    widths = c(
      1.05,
      1.35
    )
  )

save_plot(
  combo1,
  "candidate_figure_AB1C1",
  width = 15,
  height = 8
)

combo1
```

```{r combo1-downloads, echo=FALSE, results='asis'}
figure_buttons(
  "candidate_figure_AB1C1",
  "Candidate 1"
)
```

## Candidate 2 - A + scaled heatmap + multi-cell-type source-target plot

```{r combo2}
combo2 <- p_a +
  (
    p_b2 /
      p_c2
  ) +
  patchwork::plot_layout(
    widths = c(
      1.05,
      1.35
    )
  )

save_plot(
  combo2,
  "candidate_figure_AB2C2",
  width = 15,
  height = 8.5
)

combo2
```

```{r combo2-downloads, echo=FALSE, results='asis'}
figure_buttons(
  "candidate_figure_AB2C2",
  "Candidate 2"
)
```

## Candidate 3 - A + dotplot + JUN target lollipop

```{r combo3}
combo3 <- p_a +
  (
    p_b3 /
      p_c3
  ) +
  patchwork::plot_layout(
    widths = c(
      1.05,
      1.35
    )
  )

save_plot(
  combo3,
  "candidate_figure_AB3C3",
  width = 15,
  height = 8.5
)

combo3
```

```{r combo3-downloads, echo=FALSE, results='asis'}
figure_buttons(
  "candidate_figure_AB3C3",
  "Candidate 3"
)
```

# Selection tables

## TFs selected for panel B

```{r tf-selection-table}
selection_table
```

## JUN targets selected for panel C

```{r jun-target-table}
top_jun_targets
```

# Saved outputs

```{r outputs}
saved_files <- list.files(
  OUTDIR,
  recursive = TRUE,
  full.names = FALSE
)

data.frame(
  file = saved_files
)
```
